COG-ED Manuscript

### 2021-12-15 06_Paper/COG-ED/Manuscript.Rmd
changed wording in intro
adjustments to pipelines

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package

@@

@@

  # remove trials with RT < 100 ms from the n-back data and exclude trials after incorrect trials

  data_RT <- data_nback[-c(which(data_nback$rt < 0.1)), ]
  data_RT <- data_RT[-c(which(data_RT$correct == 0) + 1), ]

@@

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
A newly added hypothesis is that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

  # create new data frames for the specification curve analysis
  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
  #
  # across which dimensions the tranformation and outlier exclusion will be done:
  #   (AA) across subjects, across n-back levels
  #   (AW) across subjects, within n-back levels
  #   (WW) within subjects, within n-back levels
  #   (WA) within subjects, across n-back levels
  # RT transformations:
  #   (R) raw/none
  #   (L) log
  #   (I) inverse
  #   (S) square-root
  # RT outlier exclusion:
  #   (N) none
  #   (2) 2 MADs from the median
  #   (5) 2.5 MADs from the median
  #   (3) 3 MADs from the median
  #   (O) 0-100 ms after stimulus onset
  #   (T) 0-200 ms after stimulus onset
  #
  # Example: the data frame "AWL3" has log-transformed RT data with no data points beyond 3 MADs
  # from the median
  #
  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R__) with either no outlier
  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
  # time-based exclusion is nonsensical for transformed data sets.

@@

    # exclude RTs fast than 100 or 200 ms after stimulus onset if the fourth letter in the data frame name is an "O" or a "T"
    # also making sure that there are even any trials below 100/200 ms, otherwise you get an error message

@@

```{r Hypothesis_2b, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

@@

@@

  h2b_data <- merge(dprime[c("subject", "level", "d")], data_nback, by = c("subject", "level"))

@@

    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
                                           nfc = sum(nfc)))
  }
  data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"

@@

  # get subset for MLM

  h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)
                               & rt > 0.1))

@@

  # d'
  h2b_sub$d.cwc <- h2b_sub$d - (ave(h2b_sub$d, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

  # RT
  h2b_sub$rt.cwc <- h2b_sub$rt - (ave(h2b_sub$rt, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

  # level
  h2b_sub$level.cwc <- h2b_sub$level - (ave(h2b_sub$level, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

  # correct 
  h2b_sub$correct.cwc <- h2b_sub$correct - (ave(h2b_sub$correct, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

  # postcorrect
  h2b_sub$postcorrect.cwc <- h2b_sub$postcorrect - (ave(h2b_sub$postcorrect, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))

@@

  # NFC
  h2b_sub$nfc.cgm <- scale(h2b_sub$nfc, scale = F)

  # null model -----------------------------------------------------------------
  m0_h2b <- lmer(sv ~ 1 + (1|subject), 
                 data = h2b_sub,
                 REML = T)

@@

  ## maximal model ---- 
  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
                 data = h2b_sub,
                 REML = T) # parameters estimated by restricted log-likelihood maximization

  ## plot model fit of the final model ----
  library(sjPlot)
  plot_model(m1_h2b, type = "diag")

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit

@@

  # correct subject code
  data_nback$subject[which(data_nback$subject == "E12K08_neu")] <- "E12K08"
  data_ED$subject[which(data_ED$subject == "E12K08_neu")] <- "E12K08"

@@

@@

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
Here we added they hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

  # create new data frames for the specification curve analysis
  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
  #
  # across which dimensions the transformation and outlier exclusion will be done:
  #   (AA) across subjects, across n-back levels
  #   (AW) across subjects, within n-back levels
  #   (WW) within subjects, within n-back levels
  #   (WA) within subjects, across n-back levels
  # RT transformations:
  #   (R) raw/none
  #   (L) log
  #   (I) inverse
  #   (S) square-root
  # RT outlier exclusion:
  #   (N) none
  #   (2) 2 MADs from the median
  #   (5) 2.5 MADs from the median
  #   (3) 3 MADs from the median
  #   (O) 0-100 ms after stimulus onset
  #   (T) 0-200 ms after stimulus onset
  #
  # Example: the data frame "AWL3" has log-transformed RT data with no data points beyond 3 MADs
  # from the median
  #
  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R__) with either no outlier
  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
  # time-based exclusion is nonsensical for transformed data sets.

@@

    # exclude RTs faster than 100 or 200 ms after stimulus onset if the fourth letter in the data frame name is an "O" or a "T"
    # also making sure that there are even any trials below 100/200 ms, otherwise you get an error message

@@

```{r Hypothesis_2b_2c, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

@@

  # H2c: SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.

@@

  h2b_data <- pipelines_data[["AARO"]]

@@

@@

  # get subset for MLM without RT = NA

  h2b_data <- droplevels(subset(h2b_data[c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)))

@@

  # dprime
  h2b_data$dprime.cwc <- h2b_data$dprime - (ave(h2b_data$dprime, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))

  # RT
  h2b_data$rt.cwc <- h2b_data$rt - (ave(h2b_data$rt, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))

  # level
  h2b_data$level.cwc <- h2b_data$level - (ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))

  # correct 
  h2b_data$correct.cwc <- h2b_data$correct - (ave(h2b_data$correct, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))

  # postcorrect
  h2b_data$postcorrect.cwc <- h2b_data$postcorrect - (ave(h2b_data$postcorrect, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))

@@

  # NFC
  h2b_data$nfc.cgm <- scale(h2b_data$nfc, scale = F)

  # null model -----------------------------------------------------------------
  m0_h2b <- lmer(sv ~ 1 + (1|subject), 
                 data = h2b_data,
                 REML = T)

@@

  ## maximal model ---- 
  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
                 data = h2b_data,
                 REML = T) # parameters estimated by restricted log-likelihood maximization

  ## plot model fit of the final model ----
  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
